{\bf {\Large Title....}}

### 2016-06-29 ident_manu.Rnw
fig 2 added

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
% \usepackage{amsmath,amsfonts,amssymb,amsthm}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

source('R/funcs.r')
library(WRTDStidal)
library(tidyr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(Hmisc)
@

@@

<<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.  The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.  For example, there are six unique parameter combinations that result from choosing two parameters from a set.  Note that the number of unique combinations is shown as the natural-log.  The same information is viewed differently in each plot.', fig.height = 5, fig.width = 10, out.width = '\\textwidth'>>=

@@

pal <- 'RdYlGn'

p1 <- ggplot(toplo, aes(x = sels, y = combs, group = numparms, colour = numparms)) + 
  geom_line() +
  # geom_point() + 
  theme_minimal() + 
  scale_colour_distiller(palette = pal, 
    guide = guide_legend(title = 'Total number of\nparameters in set')) +
  scale_x_continuous('Number of parameters selected from total', expand = c(0, 0)) + 
  scale_y_continuous('Number of unique parameter combinations, log-scale', expand = c(0, 0)) + 
  theme(legend.position = 'top')

@@

grid.arrange(p1, p2, ncol = 2)
@

>>>>

\documentclass[letterpaper,12pt,oneside]{article}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

source('R/funcs.r')
library(WRTDStidal)
library(tidyr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(Hmisc)
library(ncdf4)
@

@@

% combination example
<<combnex, echo = F, fig.cap = 'Number of unique combinations that can occur by selecting parameters for optimization from different parameter sets.  The number of combinations are shown for increasing numbers of selected parameters from the total in the set, where 100 parameter sets are shown each with one through 100 total parameters.  For example, there are six unique parameter combinations that result from choosing two parameters from a set.  Note that the number of unique combinations is shown as the natural-log.  The same information is viewed differently in each plot.', fig.height = 5, fig.width = 5, out.width = '0.6\\textwidth'>>=

@@

pal <- 'RdYlGn'
# 
# p1 <- ggplot(toplo, aes(x = sels, y = combs, group = numparms, colour = numparms)) + 
#   geom_line() +
#   # geom_point() + 
#   theme_minimal() + 
#   scale_colour_distiller(palette = pal, 
#     guide = guide_legend(title = 'Total number of\nparameters in set')) +
#   scale_x_continuous('Number of parameters selected from total', expand = c(0, 0)) + 
#   scale_y_continuous('Number of unique parameter combinations, log-scale', expand = c(0, 0)) + 
#   theme(legend.position = 'top')

@@

# grid.arrange(p1, p2, ncol = 2)
p2
@

% sensitivity example of top
<<sensplo, fig.cap = 'Sensitivity of \\ac{do} to parameter changes.  Each solid line shows the parameter within each category that had the largest effect on \\ac{do} with a 50\\% change from the default value.  The dashed line shows \\ac{do} holding all parameters at their default values.  The bottom plot shows the estimated \\ac{do} as a difference from the default.', fig.height = 5.5, fig.width = 8, echo = F, cache = TRUE>>=
load(file = 'data/sens_ests.RData')
load(file = 'data/sens_ests_cat.RData')

toeval <- group_by(sens_ests_cat, Category) %>% 
  filter(error == max(error)) %>% 
  arrange(error) %>% 
  data.frame

toeval <- toeval$Parameter %>% 
  as.character

toplo <- filter(sens_ests$raw, Parameter %in% toeval) %>% 
  mutate(
    diffest = Estimate - default,
    time = as.POSIXct(time, origin = as.POSIXct('2002-01-01 0:0', tz = "GMT"), tz = 'GMT'),
    time = as.Date(time)
  )

ylab <- expression(paste(O[2], ' (mmol ', m^-3, ')'))
colset <- 'Set2'
lnsz <- 1
alph <- 0.8

leglabs <- list(
  expression(atop('Optics', italic(astar490))),
  expression(atop('Organic Matter', italic('k11'))),
  expression(atop('Phytoplankton', italic(Qc[italic('p1')]))),
  expression(atop('Temperature', italic(Tref(nospA+nospZ)[italic('p4')]))),
  expression(atop('Zooplankton', italic(Zka[italic('p1')])))
  )

p1 <- ggplot(toplo, aes(x = time, y = Estimate, group = Parameter, colour = Parameter)) + 
  geom_line(aes(y = default), colour = 'black', linetype = 'dashed') + 
  geom_line(size = lnsz, alpha = alph) + 
  theme_minimal() +
  scale_colour_brewer(palette = colset, 
    labels = leglabs
    ) + 
  scale_y_continuous(ylab) + 
  theme(
    legend.position = 'top',
    axis.text.x = element_blank(), 
    axis.title.x = element_blank(),
    axis.line.x = element_line(), 
    axis.line.y = element_line()
    )

p2 <- ggplot(toplo, aes(x = time, y = diffest, group = Parameter, colour = Parameter)) + 
  geom_hline(yintercept = 0, linetype = 'dashed') +
  geom_line(size = lnsz, alpha = alph) + 
  theme_minimal() +
  scale_colour_brewer(palette = colset) + 
  scale_y_continuous('Difference') + 
  theme(
    legend.position = 'none',
    axis.title.x = element_blank(),
    axis.line.x = element_line(), 
    axis.line.y = element_line()
    )

# align widths of plots in first column, first two
pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3])

# Set the widths
pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth

grid.arrange(pA, pB, ncol = 1, heights = c(1, 0.85))
@

### 2016-06-29 ident_manu.tex
fig 2 added

\usepackage{alltt}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
% \usepackage{amsmath,amsfonts,amssymb,amsthm}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Tue Jun 28 11:58:04 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\begin{figure}[!ht]

{\centering \includegraphics[width=\textwidth]{figs/combnex-1}

@@

@@

%latex.default(totab, file = "", rowlabel = "Parameter", caption = cap.val,     caption.loc = "top", rowname = Parameter, label = "tab:optsens")%
\begin{table}[!tbp]
\caption{Test\label{tab:optsens}} 
\begin{center}
\begin{tabular}{llrll}
\hline\hline
\multicolumn{1}{l}{Parameter}&\multicolumn{1}{c}{Description}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
\textit{astar490}&Chla specific absorption at 490 nm&$0.0375$&$1.64$&$8.64$\tabularnewline
\textit{astarOMA}&OM\_A specific absorption at 490 nm&$0.1000$&$2.29\times 10^{-2}$&$9.52\times 10^{-2}$\tabularnewline
\textit{astarOMZ}&OM\_Z specific absorption at 490 nm&$0.1000$&$5.65\times 10^{-3}$&$1.42\times 10^{-2}$\tabularnewline
\textit{Kcdom}&AOP, light attenuation due to CDOM&$0.0010$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
\hline
\end{tabular}\end{center}

>>>>

\usepackage{alltt}
\usepackage[paperwidth=8.5in,paperheight=11in,top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{setspace}
\usepackage[colorlinks=true,allcolors=Blue]{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{indentfirst}
\usepackage{titlesec}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{outlines}
\usepackage{lineno}
\usepackage{array}
\usepackage{times}
\usepackage{cleveref}
\usepackage{acronym}
\usepackage[position=t]{subfig}
\usepackage{paralist}
\usepackage[noae]{Sweave}
\usepackage{natbib}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{bm}
\usepackage{fixltx2e}
% \usepackage{showlabels}
\bibpunct{(}{)}{,}{a}{}{,}

@@

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Jun 29 14:50:46 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

% combination example
\begin{figure}[!ht]

{\centering \includegraphics[width=0.6\textwidth]{figs/combnex-1}

@@

% sensitivity example of top
\begin{figure}[!ht]

{\centering \includegraphics[width=\maxwidth]{figs/sensplo-1}

\caption{Sensitivity of \ac{do} to parameter changes.  Each solid line shows the parameter within each category that had the largest effect on \ac{do} with a 50\% change from the default value.  The dashed line shows \ac{do} holding all parameters at their default values.  The bottom plot shows the estimated \ac{do} as a difference from the default.}\label{fig:sensplo}
\end{figure}

@@

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of optics parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.\label{tab:optsens}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
Chla specific absorption at 490 nm&\textit{astar490}&$0.04$&$1.64$&$8.64$\tabularnewline
OMA specific absorption at 490 nm&\textit{astarOMA}&$0.1$&$0.02$&$0.1$\tabularnewline
OMZ specific absorption at 490 nm&\textit{astarOMZ}&$0.1$&$0.01$&$0.01$\tabularnewline
AOP, light attenuation due to CDOM&\textit{Kcdom}&$0$&$3.18\times 10^{-6}$&$1.09\times 10^{-5}$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of temperature parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:tempsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{Optimum temperature for growth(C)}&&&\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P4}}&$17$&$2.9$&$22.95$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{Z2}}&$26$&$0.18$&$2.59$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P5}}&$26$&$0.17$&$0.72$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P2}}&$22$&$0.16$&$0.82$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{Z1}}&$22$&$0.16$&$0.33$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P3}}&$17$&$0.14$&$0.78$\tabularnewline
~~\textit{Tref(nospA+nospZ)\textsubscript{P1}}&$22$&$0.12$&$0.29$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of phytoplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter. Parameters less than the 75\textsuperscript{th} percentile (0.59) for L1 were removed for brevity.\label{tab:phytosens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{coefficient for non-limiting nutrient}&&&\tabularnewline
~~\textit{aN\textsubscript{P1}}&$1$&$2.7$&$47.26$\tabularnewline
~~\textit{aN\textsubscript{P3}}&$1$&$0.66$&$3.16$\tabularnewline
\hline
{half-saturation constant for N}&&&\tabularnewline
~~\textit{Kn\textsubscript{P3}}&$5.93$&$1.15$&$9.22$\tabularnewline
~~\textit{Kn\textsubscript{P4}}&$1.13$&$0.62$&$2.5$\tabularnewline
\hline
{initial slope of the photosynthesis-irradiance relationship}&&&\tabularnewline
~~\textit{alpha\textsubscript{P4}}&$3.96\times 10^{-16}$&$1.61$&$7.46$\tabularnewline
~~\textit{alpha\textsubscript{P3}}&$6.19\times 10^{-17}$&$1.06$&$3.74$\tabularnewline
~~\textit{alpha\textsubscript{P5}}&$3.87\times 10^{-16}$&$0.81$&$5.54$\tabularnewline
\hline
{minimum N cell-quota}&&&\tabularnewline
~~\textit{QminN\textsubscript{P3}}&$1.27\times 10^{-8}$&$1.53$&$6.4$\tabularnewline
~~\textit{QminN\textsubscript{P4}}&$1.53\times 10^{-10}$&$0.91$&$2.76$\tabularnewline
~~\textit{QminN\textsubscript{P1}}&$6.08\times 10^{-9}$&$0.62$&$4.55$\tabularnewline
\hline
{mortality coefficient}&&&\tabularnewline
~~\textit{mA\textsubscript{P3}}&$0.03$&$2.98$&$14.34$\tabularnewline
~~\textit{mA\textsubscript{P4}}&$0.11$&$1.35$&$7.04$\tabularnewline
\hline
{N-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxN\textsubscript{P5}}&$1.4\times 10^{-9}$&$7.57$&$43.9$\tabularnewline
~~\textit{vmaxN\textsubscript{P4}}&$1.33\times 10^{-9}$&$2.88$&$16.56$\tabularnewline
~~\textit{vmaxN\textsubscript{P3}}&$8.11\times 10^{-8}$&$1.99$&$15.23$\tabularnewline
~~\textit{vmaxN\textsubscript{P1}}&$4.1\times 10^{-8}$&$0.84$&$2.92$\tabularnewline
\hline
{P-uptake rate measured at umax}&&&\tabularnewline
~~\textit{vmaxP\textsubscript{P3}}&$6.15\times 10^{-8}$&$2.23$&$9.89$\tabularnewline
~~\textit{vmaxP\textsubscript{P1}}&$2.68\times 10^{-8}$&$0.74$&$11.41$\tabularnewline
\hline
{phytoplankton basal respiration coefficient}&&&\tabularnewline
~~\textit{respb\textsubscript{P4}}&$0.02$&$3.1$&$26.48$\tabularnewline
~~\textit{respb\textsubscript{P3}}&$0.02$&$2.15$&$6.35$\tabularnewline
~~\textit{respb\textsubscript{P5}}&$0.02$&$0.81$&$8.61$\tabularnewline
\hline
{phytoplankton carbon/cell}&&&\tabularnewline
~~\textit{Qc\textsubscript{P1}}&$1.35\times 10^{-6}$&$328.35$&$2181.05$\tabularnewline
~~\textit{Qc\textsubscript{P3}}&$2.65\times 10^{-6}$&$232.8$&$1574.72$\tabularnewline
~~\textit{Qc\textsubscript{P2}}&$1.68\times 10^{-7}$&$4.08$&$61.25$\tabularnewline
~~\textit{Qc\textsubscript{P4}}&$4.54\times 10^{-8}$&$1.03$&$3.75$\tabularnewline
\hline
{phytoplankton growth respiration coefficient}&&&\tabularnewline
~~\textit{respg\textsubscript{P4}}&$0.1$&$0.98$&$7.37$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description, Parameter",     caption = cap.val, caption.loc = "top", rgroup = unique(Description),     n.rgroup = as.numeric(table(Description)), rgroupTexCmd = NULL,     rowname = Parameter, size = tabsize, label = paste0("tab:",         tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of zooplankton parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.  Subscripts show the phytoplankton or zooplankton group that applies for the parameter.\label{tab:zoopsens}} 
\begin{center}
\begin{tabular}{llll}
\hline\hline
\multicolumn{1}{l}{Description, Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
{assimilation efficiency as a fraction of ingestion}&&&\tabularnewline
~~\textit{Zeffic\textsubscript{P1}}&$0.4$&$0.23$&$0.55$\tabularnewline
~~\textit{Zeffic\textsubscript{P2}}&$0.4$&$0.21$&$0.75$\tabularnewline
\hline
{half saturation coefficient for grazing}&&&\tabularnewline
~~\textit{ZKa\textsubscript{P1}}&$1.12\times 10^{12}$&$0.82$&$6.29$\tabularnewline
~~\textit{ZKa\textsubscript{P2}}&$1.12\times 10^{12}$&$0.46$&$3.24$\tabularnewline
\hline
{maximum growth rate of zooplankton}&&&\tabularnewline
~~\textit{Zumax\textsubscript{P2}}&$2.98\times 10^{7}$&$0.48$&$1.84$\tabularnewline
~~\textit{Zumax\textsubscript{P1}}&$9.45\times 10^{8}$&$0.46$&$0.91$\tabularnewline
\hline
{proportion of grazed phytoplankton lost to sloppy feeding}&&&\tabularnewline
~~\textit{Zslop\textsubscript{P1}}&$0.25$&$0.12$&$0.33$\tabularnewline
\hline
{Zooplankton biomass-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespb\textsubscript{P1}}&$0.1$&$0.45$&$3.02$\tabularnewline
~~\textit{Zrespb\textsubscript{P2}}&$0.42$&$0.09$&$1.05$\tabularnewline
\hline
{zooplankton carbon/individual}&&&\tabularnewline
~~\textit{ZQc\textsubscript{P2}}&$7.08\times 10^{-7}$&$0.1$&$0.36$\tabularnewline
~~\textit{ZQc\textsubscript{P1}}&$3.13\times 10^{-4}$&$0.06$&$0.62$\tabularnewline
\hline
{Zooplankton growth-dependent respiration factor}&&&\tabularnewline
~~\textit{Zrespg\textsubscript{P1}}&$0.2$&$0.24$&$3.19$\tabularnewline
~~\textit{Zrespg\textsubscript{P2}}&$0.3$&$0.12$&$0.31$\tabularnewline
\hline
{Zooplankton mortality constant for quadratic mortality}&&&\tabularnewline
~~\textit{Zm\textsubscript{P2}}&$7.2\times 10^{-4}$&$0.33$&$2.85$\tabularnewline
~~\textit{Zm\textsubscript{P1}}&$7.2\times 10^{-4}$&$0.26$&$0.8$\tabularnewline
\hline
{zooplankton nitrogen/individual}&&&\tabularnewline
~~\textit{ZQn\textsubscript{P1}}&$6.95\times 10^{-5}$&$0.47$&$1.64$\tabularnewline
~~\textit{ZQn\textsubscript{P2}}&$1.57\times 10^{-7}$&$0.24$&$1.35$\tabularnewline
\hline
{zooplankton phosphorus/individual}&&&\tabularnewline
~~\textit{ZQp\textsubscript{P2}}&$8.53\times 10^{-9}$&$0.01$&$0.01$\tabularnewline
~~\textit{ZQp\textsubscript{P1}}&$3.77\times 10^{-6}$&$0$&$0$\tabularnewline
\hline
\end{tabular}\end{center}}

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, size = tabsize,     label = paste0("tab:", tablab))%
\begin{table}[!tbp]
{\normalsize
\caption{Sensitivities of \ac{do} to perturbation of organic matter parameters.  Sensitivities are based on a 50\% increase from the default parameter value, where $L1$ and $L2$ summarize differences in model output from the default (see \cref{l1,l2}).  Parameters that did not affect \ac{do} are not shown.\label{tab:omsens}} 
\begin{center}
\begin{tabular}{lllll}
\hline\hline
\multicolumn{1}{l}{Description}&\multicolumn{1}{c}{Parameter}&\multicolumn{1}{c}{Value}&\multicolumn{1}{c}{L1}&\multicolumn{1}{c}{L2}\tabularnewline
\hline
rate constant for nitrification&\textit{k11}&$5$&$2.11$&$16.1$\tabularnewline
O2 concentration that inhibits denitrification&\textit{KstarO2}&$10$&$1.91$&$11.76$\tabularnewline
turnover rate for OM1A and OM1G&\textit{KG1}&$50$&$1.49$&$6.83$\tabularnewline
turnover rate for OM2A and OM2G&\textit{KG2}&$50$&$1.37$&$3.46$\tabularnewline
half-saturation concentration for NO3 used in denitrification&\textit{KNO3}&$10$&$1.24$&$7.98$\tabularnewline
half-saturation concentration for O2 utilization&\textit{KO2}&$10$&$0.56$&$1.92$\tabularnewline
decay rate of CDOM, 1/day&\textit{KGcdom}&$0.01$&$0.01$&$0.03$\tabularnewline
\hline
\end{tabular}\end{center}}
